A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-30 manuscript.Rmd
code is R code by default
rearrange headings

This tutorial walks through the creation of such a document that can be reproduced automatically.
Though reproducibility is a small part of the research process, it can serve as the mortar of open science building blocks (e.g. preregistration, open data, postpublication review).
Therefore, we show the whole lifecycle of an open research project, where some parts are essential to archive reproducibility.
All code chunks are meant for the reader to try out for themselves.
Still, the reader can safely skip sections marked as optional when unfit for their research question or methods.
However, any empirical data analysis will suffer from the following threats to reproducibility:
<!-- Which problems are solved by which tool (like in Andreas talk)-->
<!--stolen from: https://brandmaier.github.io/reproducible-data-analysis-materials/KULeuvenQuantPsy2020.html#11 -->

@@

@@

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `missing_rcode_simulation` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `missing_rcode_simulation`%.
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.

@@

<!--Hands on: Introduce R Markdown-->
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Literate programming combines code and text, enabling you to explain your reasoning.
As @knuthCWEBSystemStructured states: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
We already learned about [Markdown], to write text.
R Markdown allows you to include R code (in fact, arbitrary computer code; see @riedererChapter15Other).
To create an R Markdown document, click on:

@@

@@

@@

@@

## Creating a public release

@@

## Releasing a Preprint (optional)

<!-- Hands on: add commit hash to results-->
<!-- Hands on: git tag + github release-->

# Peer Review (optional)

# Post Publication Review (optional)

# Archiving

<!-- Hands on: explain how to archive data-->
<!-- Hands on: explain how to archive docker images-->

>>>>

This tutorial walks through the creation of such a document that can be reproduced automatically.
Though reproducibility is a small part of the research process, it can serve as the mortar of open science building blocks (e.g. preregistration, open data, postpublication review).
Therefore, we show the whole lifecycle of an open research project, where some parts are essential to archive reproducibility.
All code chunks are meant for the reader to try out for themselves.
If not declared otherwise the code is meant to run in R (version `r with(R.version, paste0(major, ".", minor))`).
Still, the reader can safely skip sections marked as optional when unfit for their research question or methods.
However, any empirical data analysis will suffer from the following threats to reproducibility:
<!-- Which problems are solved by which tool (like in Andreas talk)-->
<!--stolen from: https://brandmaier.github.io/reproducible-data-analysis-materials/KULeuvenQuantPsy2020.html#11 -->

@@

### Preregistration as Code

@@

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `missing_rcode_simulation` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `missing_rcode_simulation`%.
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.

@@

<!--Hands on: Introduce R Markdown-->
As @knuthCWEBSystemStructured states: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
We already learned about [Markdown], to write text.
R Markdown allows you to include R code (in fact, arbitrary computer code; see @riedererChapter15Other).
To create an R Markdown document, click on:

@@

### README (optional)

@@

### License

@@

### Code of Conduct

@@

@@

# Creating a public release

<!-- public releases like preregistration, preprint -->
<!-- Hands on: add commit hash to results-->
<!-- Hands on: git tag + github release-->
<!-- Hands on: explain how to archive data-->
<!-- Hands on: explain how to archive docker images-->
